Visualizations for the manuscript

### 2022-06-01 metanalysis_visualization/manuscript_Figures.Rmd
update lef pannel to % and reverse heatmap from high to low

pvalues_boot <- bootstrapped_coefficients_all %>% 
  group_by(siteid, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Coefficient difference: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

pvalues_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Coefficient difference: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 3, eps = 10**-3), ")")
  )

@@

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

@@

pvalues_boot_disorders <- bootstrapped_coefficients_disorders %>% 
  group_by(disorder_group, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Coefficient difference: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

fig <- fig %>%
  layout(
    title = " ",
    xaxis = list(
      type = 'date',
      tickformat = "%b-%y", 
      tickangle=-45, 
      tickvals=dates), 
    shapes = list(vline(as.Date("2020-03-15"))))

fig
#plotly::orca(fig, file = "figure_supp3_counts_disorder.png")
```

@@

numberOfCodesPerDisorderGroup %>%
  left_join( country_map ) %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
ggsave("figure_supp2_ICDdictionaryQC.png", height = 20, width = 45, units = "cm")

@@

counts2 <- reshape2::melt(counts ,  id.vars = c('plotsLabel', 'time_p', 'time','month_year'), variable.name = 'group')
counts2$group <- gsub("count_psy_patients", "patients with psychiatric conditions", counts2$group )
counts2$group <- gsub("total_cases", "total number of patients", counts2$group )

@@

counts_agg2 <- reshape2::melt(counts_agg ,  id.vars = c('time_p', 'time','month_year'), variable.name = 'group')
counts_agg2$group <- gsub("count_psy_patients", "patients with psychiatric conditions", counts_agg2$group )
counts_agg2$group <- gsub("total_cases", "total number of patients", counts_agg2$group )

>>>>

pvalues_boot <- bootstrapped_coefficients_all %>% 
  group_by(siteid, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("",
                        observed_slope_coefficient,
                        "% (p-value: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

pvalues_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("",
                        observed_slope_coefficient,
                        "% (p-value: ",
                        format.pval(pvalue, digits = 3, eps = 10**-3), ")")
  )

@@

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  #scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

@@

pvalues_boot_disorders <- bootstrapped_coefficients_disorders %>% 
  group_by(disorder_group, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("",
                        observed_slope_coefficient,
                        "% (p-value: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

fig <- fig %>%
  layout(
    title = " ",
      yaxis = list(autorange="reversed"), 
    xaxis = list(
      type = 'date',
      tickformat = "%b-%y", 
      tickangle=-45, 
      tickvals=dates), 
    shapes = list(vline(as.Date("2020-03-15"))))

fig

#plotly::orca(fig, file = "figure_supp3_counts_disorder.png")
```

@@

numberOfCodesPerDisorderGroup %>%
  left_join( country_map ) %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "Number of ICD-10 codes") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
ggsave("figure_supp2_ICDdictionaryQC.png", height = 20, width = 45, units = "cm")

@@

counts2 <- reshape2::melt(counts ,  id.vars = c('plotsLabel', 'time_p', 'time','month_year'), variable.name = 'group')
counts2$group <- gsub("count_psy_patients", "Patients with mental health disorder", counts2$group )
counts2$group <- gsub("total_cases", "Total number of patients", counts2$group )

@@

counts_agg2 <- reshape2::melt(counts_agg ,  id.vars = c('time_p', 'time','month_year'), variable.name = 'group')
counts_agg2$group <- gsub("count_psy_patients", "Patients with mental health disorder", counts_agg2$group )
counts_agg2$group <- gsub("total_cases", "Total number of patients", counts_agg2$group )
